Deep Reinforcement Learning for Conservation Decisions

### 2022-06-03 manuscript/manuscript.Rmd
slight tweak

This paper does not intend to validate deep RL as a method that should be used to directly inform decision-making on current conservation problems.
Instead, we have selected example problems to provide ecologists with a greater background to engage in the collaborative development of deep RL-based methods, while also highlighting challenges which ecological problems pose to existing techniques.
Validating deep RL for current conservation problems is beyond the scope of any one paper: this will necessitate examining a range of more "precise" models which will require more computational resources than is available to most researchers and extensive collaboration between large teams of ecologists and computer scientists.

>>>>

This paper does not intend to validate deep RL as a method that should be used to directly inform decision-making on current conservation problems.
Rather, we seek to provide ecologists with a greater understanding of both potentials and pitfalls of this emerging approach. 
We have selected familiar example problems to provide ecologists with a greater background and intuition to understand these techniques and engage in the collaborative development of deep RL-based methods, while also highlighting challenges which ecological problems pose to existing techniques.
Validating deep RL for current conservation problems is beyond the scope of any one paper: this will necessitate examining a range of more "precise" models which will require more computational resources than is available to most researchers and extensive collaboration between large teams of ecologists and computer scientists.
